Holomorphic M-theory and the $\SU(4)$-invariant twist of type $\IIA$

### 2020-09-29 BCOV with potentials/BCOV with potentials.tex
small changes

Let $X$ be a Calabi--Yau surface. 
Minimal Kodaira--Spencer theory is a $\mb Z/2$-graded theory described by two fundamental sets of fields:
\begin{itemize}
\item An odd field given by a divergence-free holomorphic vector field $\mu^1$. 
\item An even field given by a holomorphic function $\mu^0$.
\end{itemize}
These fields combine to define a $\mb Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$. 
There is a Lie algebra structure the parity reversed sheaf $\Pi \mc E^{\rm hol}$ using the Lie bracket of holomorphic vector fields together with the natural action of holomorphic vector fields on holomorphic functions.

The sheaf $\mc E^{\rm hol}$ admits the following locally free description:
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} \\
 & \PV^{0,\bu} \\
 \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} .
\end{tikzcd}
\]
We refer to this locally free description by $\mc E$. 
The Lie bracket on $\Pi \mc E^{\rm hol}$ described above extends to a Lie bracket on $\Pi \mc E$.
Together with the differential this gives $\Pi \mc E$ the structure of a local dg Lie algebra.

@@

%\iffalse
Let \(X\) be a CY4. BCOV theory on \(X\) with potentials will be the \(\mb{Z}/2\) graded BV theory defined as follows. Fix splittings \(C_1: (\im\del\subset\PV^{3,\bullet})\to \PV^{4,\bullet}\) of  \[0\to\ker\del\to \PV^{4,\bullet}\to(\im\del\subset\PV^{3,\bullet}\to 0\] and \(C_2: (\im\del\subset\PV^{2,\bullet})\to\PV^{3,\bullet}\) of \[0\to\ker\del\to\PV^{3,\bullet}\to(\im\del\subset\PV^{2,\bullet}(X))\to 0.\] And let \(\phi_{C_1} : \PV^{4,\bullet}\cong(\ker\del\subset\PV^{4,\bullet})\oplus(\im\del\subset\PV^{3,\bullet})\), \(\phi_{C_2}: \PV^{3,\bullet}\cong(\ker\del\subset\PV^{3,\bullet})\oplus(\im\del\subset\PV^{2,\bullet})\) be the resulting isomorphisms.
\begin{itemize}
\item The fields of the theory are
 \[\begin{aligned} \mc E_{mBCOV}^{C_1,C_2} = \PV^{0,\bullet} \oplus (\ker\del\subset\PV^{1,\bullet})\oplus & (\im\del\subset\PV^{2,\bullet} \oplus\ker\del\subset\PV^{3,\bullet})\\ \oplus &(\im\del\subset\PV^{3,\bullet}\oplus\ker\del\subset\PV^{4,\bullet})\end{aligned}\]
\item The Poisson kernel is given by $(\del\otimes 1)\delta_{Diag}$
\item The \(L_\infty\) structure is defined as follows
\begin{itemize}
\item \(\ell_1=\delbar\)
\item \(\ell_2\) is a certain modification of the Schouten bracket, defined as follows. Let \([-,-]\) denote the usual Schouten bracket of polyvector fields. Then

@@

\begin{rmk}
\begin{itemize}
\item Note that the complex underlying $\mc E_{mBCOV}^{C_1,C_2}$ does not arise as sections of a graded vector bundle due to the presence of the constraints.
\item Recall that minimal BCOV theory has fields $\mc E_{mBCOV}=\oplus_{i\leq 3} (\ker\del\subset\PV^{\i,\bullet}$. As we have mentioned above, we may view the underlying complex of $\mc E_{mBCOV}^{C_1,C_2}$ as gotten by replacing $\ker\del\subset\PV^{2/3,\bullet}\subset\mc E_{mBCOV}$ with $\PV^{3/4,\bullet}$ in the same degree, and using the isomorphisms $\phi_{C_1,C_2}$. The $L_\infty$ structure is gotten by simply transporting the ordinary Schouten-Nijenhuis bracket on \[\PV^{0,\bullet}\oplus(\ker\del\subset\PV^{1,\bullet}\oplus\PV^{3,\bullet}[]\oplus\PV^{4,\bullet}[]\] and applying the fact that since $\del$ is a derivation of $[-,-]$, for $\mu\in\ker\del$, $[\mu,\del\gamma]=(-1)^{|\mu|-1}\del[\mu,\gamma]$ and $[\del\gamma,\mu]=\del[\gamma,\mu]$. Hopefully this demystifies the above formulas.
\item Suppose we were to naively try to define a BV pairing $\omega$ on $\mc E_{mBCOV}^{C_1,C_2}$ by $\omega(-,-)=\int (-)\wedge\del^{-1}(-)$ and write an "action functional" using the above $L_\infty$-structure. Then the resulting action functional would be equivalent to one coming from an honest BV pairing and an $L_\infty$-structure involving a composition of $\del$ and the ordinary Schouten-Nijenhuis bracket. Note that we could have accomplished the same thing by choosing splittings of $\del$ from any $\im\del\subset \PV^{d_1,\bullet}$, $\im\del\subset\PV^{d_2,\bullet}$ such that $d_1+d_2\neq d-1$. However, it seems like these two choices of splittings are favored in a sense (articulated below). 
\end{itemize}
\end{rmk}
%\fi

\section{Dimensional Reduction}
Let's consider the holomorphic twist of M-theory on $\R\times\C^\times\times\C^4$. We may decompose the fields as
\begin{itemize}
\item \[(\mu^{1}, \mu^{0})=(\mu_{01}+\mu_{10}, \mu^{0})\in\Omega^\bullet(\R)\otimes\left (\begin{aligned} &( \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4)) \\ \oplus & (\PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4))\end{aligned} \to\PV^{0,\bullet}(\C^\times\times\C^4)\right ).\]
\item $\gamma=\gamma_{01}+\gamma_{10}\in \Omega^\bullet(\R)\otimes(\Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\oplus\Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4))$.
\end{itemize}

@@

>>>>

Let $X$ be a Calabi--Yau surface. 
Minimal Kodaira--Spencer theory is a $\mb Z/2$-graded Poisson BV theory described by two fundamental sets of fields:
\begin{itemize}
\item An odd field given by a divergence-free holomorphic vector field $\mu^1$. 
\item An even field given by a holomorphic function $\mu^0$.
\end{itemize}
These fields combine to define a $\mb Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$. 
There is a Lie algebra structure the parity reversed sheaf $\Pi \mc E^{\rm hol}$ using the Lie bracket of holomorphic vector fields together with the natural action of holomorphic vector fields on holomorphic functions.

The sheaf $\mc E^{\rm hol}$ admits the following locally free description:
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} \\
 & \PV^{0,\bu} \\
 \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} .
\end{tikzcd}
\]
We refer to this locally free description by $\mc E$. 
The Lie bracket on $\Pi \mc E^{\rm hol}$ described above extends to a Lie bracket on $\Pi \mc E$.
Together with the differential this gives $\Pi \mc E$ the structure of a local dg Lie algebra.

@@

\iffalse
Let \(X\) be a CY4. BCOV theory on \(X\) with potentials will be the \(\mb{Z}/2\) graded BV theory defined as follows. Fix splittings \(C_1: (\im\del\subset\PV^{3,\bullet})\to \PV^{4,\bullet}\) of  \[0\to\ker\del\to \PV^{4,\bullet}\to(\im\del\subset\PV^{3,\bullet}\to 0\] and \(C_2: (\im\del\subset\PV^{2,\bullet})\to\PV^{3,\bullet}\) of \[0\to\ker\del\to\PV^{3,\bullet}\to(\im\del\subset\PV^{2,\bullet}(X))\to 0.\] And let \(\phi_{C_1} : \PV^{4,\bullet}\cong(\ker\del\subset\PV^{4,\bullet})\oplus(\im\del\subset\PV^{3,\bullet})\), \(\phi_{C_2}: \PV^{3,\bullet}\cong(\ker\del\subset\PV^{3,\bullet})\oplus(\im\del\subset\PV^{2,\bullet})\) be the resulting isomorphisms.
\begin{itemize}
\item The fields of the theory are
 \[\begin{aligned} \mc E_{mBCOV}^{C_1,C_2} = \PV^{0,\bullet} \oplus (\ker\del\subset\PV^{1,\bullet})\oplus & (\im\del\subset\PV^{2,\bullet} \oplus\ker\del\subset\PV^{3,\bullet})\\ \oplus &(\im\del\subset\PV^{3,\bullet}\oplus\ker\del\subset\PV^{4,\bullet})\end{aligned}\]
\item The Poisson kernel is given by $(\del\otimes 1)\delta_{Diag}$
\item The \(L_\infty\) structure is defined as follows
\begin{itemize}
\item \(\ell_1=\delbar\)
\item \(\ell_2\) is a certain modification of the Schouten bracket, defined as follows. Let \([-,-]\) denote the usual Schouten bracket of polyvector fields. Then

@@

\begin{rmk}
\begin{itemize}
\item Note that the complex underlying $\mc E_{mBCOV}^{C_1,C_2}$ does not arise as sections of a graded vector bundle due to the presence of the constraints.
\item Recall that minimal BCOV theory has fields $\mc E_{mBCOV}=\oplus_{i\leq 3} (\ker\del\subset\PV^{\i,\bullet}$. As we have mentioned above, we may view the underlying complex of $\mc E_{mBCOV}^{C_1,C_2}$ as gotten by replacing $\ker\del\subset\PV^{2/3,\bullet}\subset\mc E_{mBCOV}$ with $\PV^{3/4,\bullet}$ in the same degree, and using the isomorphisms $\phi_{C_1,C_2}$. The $L_\infty$ structure is gotten by simply transporting the ordinary Schouten-Nijenhuis bracket on \[\PV^{0,\bullet}\oplus(\ker\del\subset\PV^{1,\bullet}\oplus\PV^{3,\bullet}[]\oplus\PV^{4,\bullet}[]\] and applying the fact that since $\del$ is a derivation of $[-,-]$, for $\mu\in\ker\del$, $[\mu,\del\gamma]=(-1)^{|\mu|-1}\del[\mu,\gamma]$ and $[\del\gamma,\mu]=\del[\gamma,\mu]$. Hopefully this demystifies the above formulas.
\item Suppose we were to naively try to define a BV pairing $\omega$ on $\mc E_{mBCOV}^{C_1,C_2}$ by $\omega(-,-)=\int (-)\wedge\del^{-1}(-)$ and write an "action functional" using the above $L_\infty$-structure. Then the resulting action functional would be equivalent to one coming from an honest BV pairing and an $L_\infty$-structure involving a composition of $\del$ and the ordinary Schouten-Nijenhuis bracket. Note that we could have accomplished the same thing by choosing splittings of $\del$ from any $\im\del\subset \PV^{d_1,\bullet}$, $\im\del\subset\PV^{d_2,\bullet}$ such that $d_1+d_2\neq d-1$. However, it seems like these two choices of splittings are favored in a sense (articulated below). 
\end{itemize}
\end{rmk}
\fi

\section{Dimensional Reduction}
Let's consider the $11$-dimensional theory on the manifold
\[
\R\times\C^\times\times\C^4 .
\]

The fields decompose as follows.
For the ``base" direction, fields we labeled by $\mu$, we have
\[
\mu = \begin{pmatrix} \mu_{01} \\ \mu_{10} \end{pmatrix} + u \mu_{11d}^0 \in \left (\begin{aligned} & \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4) \\ \oplus & \PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4)\end{aligned} \to u \PV^{0,\bullet}(\C^\times\times\C^4)\right ) \Hat{\otimes} \Omega^\bullet(\R) [1] .
\]

For the ``fiber" direction, fields we labeled by $\gamma$, we have
\[
\gamma = u^{-1} \gamma_{11d}^0 + \begin{pmatrix} \gamma_{01} \\ \gamma_{10} \end{pmatrix} \in \left (u^{-1} \Omega^{0,\bullet}(\C^\times\times\C^4) \to \begin{aligned} & \Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\\ \oplus & \Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4)\end{aligned} \right ) \Hat{\otimes} \Omega^\bullet(\R).
\]

The ``zero modes" of the reduction along the circle $S^1 \subset \mb C^\times$ will be denoted by the same symbols.
\brian{write down this sheaf on $\mb C^4 \times \mb R^2$.}

Define the map of sheaves of cochain complexes 
\[
\Psi : \pi_* \mc E_{11d} \to \mc E_{\rm pot} \Hat{\otimes} \Omega^\bu(\mb R^2) 
\] 
by
\[
\begin{array}{cccccccc}
\Psi (\mu_{01}) & = & \mu_{01} & \in & \PV^{1,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) \\
\Psi (\mu_{10}) & = & \mu_{10} \vee \Omega^{-1}_{\mb C^4} & \in & \PV^{4,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) .
\end{array}
\]

%\[
%\gamma=\gamma_{01}+\gamma_{10}\in \Omega^\bullet(\R)\otimes(\Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\oplus\Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4)) .
%\]

@@

\section{Compactification to five dimensions}

Now, consider placing the $11$-dimensional theory on the manifold
\[
X \times Y \times \mb R 
\]
where $X$ is compact Calabi--Yau three-fold and $Y$ is a Calabi--Yau surface.
We consider the compactification of the theory along the projection map 
\[
\pi : X \times Y \times \mb R \to Y \times \mb R .
\]
Recall, the space of fields of the $11$-dimensional theory is
\begin{equation}\label{eqn:cotangent1}
T^* [-1] \bigg(\PV^{\leq 1,\bu}(X \times Y) \Hat{\otimes} \Omega^\bu(\mb R) [1] \bigg) .
\end{equation}

Since $X$ is compact and Calabi--Yau, we have a sequence of quasi-isomorphisms 
\[
\PV^{j, \bu}(X) \cong_{\Omega_X} \Omega^{3-j, \bu} (X) \simeq H^{3-j, \bu}(X) .
\]
The first isomorphism is simply contraction with the Calabi--Yau form $\Omega_X \in \Omega^{3,hol}(X)$ and the second quasi-isomorphism follows from formality of $X$.

In particular, at the level of sheaves one has a quasi-isomorphism
\[
\pi_* \bigg(\PV^{\leq 1,\bu}(X \times Y) \Hat{\otimes} \Omega^\bu(\mb R) [1] \bigg) \simeq H^{\geq 2, \bu}(X) \otimes \PV^{\leq 1, \bu} (Y) \Hat{\otimes} \Omega^\bu (\mb R) [1] .
\]
This describes the ``base" direction, fields we labeled by $\mu$, of the space of fields (\ref{eqn:cotangent1}) upon compactification.

We extract the piece of the above sheaf which involves the top cohomology $H^{3,3}(X) \cong H^6(X) \cong \mb C$. 
This is the sheaf
\begin{equation}\label{eqn:pair1}
\PV^{\leq 1, \bu}(Y) \Hat{\otimes} \Omega^\bu (\mb R) [1] .
\end{equation}
(Recall, we are only working with sheaves of $\mb Z/2$-graded cochain complexes.)

Likewise, the ``fiber" direction of (\ref{eqn:cotangent1}) becomes, after compactification:
\[
\pi_* \bigg(\Omega^{\leq 1, \bu}(X \times Y) \Hat{\otimes} \Omega^\bu(\mb R) \bigg) \simeq H^{\leq 1, \bu}(X) \otimes \Omega^{\leq 1, \bu} (X) \Hat{\otimes} \Omega^\bu (\mb R)  .
\]
Under the BV pairing, the piece of this sheaf of cochain complexes with (\ref{eqn:pair1}) is the part involving $H^0(X) \cong \mb C$.
This is precisely
\[
\Omega^{\leq 1}(X) \Hat{\otimes} \Omega^\bu (\mb R) .
\]
